\begin{thebibliography}{10}

%%examples:
%%Book
%\bibitem{amsbook}
%F. Mittelbach et al.
%\newblock {\em The LaTeX Companion, 2nd ed}.
%\newblock Addison-Wesley, 2004.
%
%%Journal paper
%\bibitem{gned:43}
%B.~V. Gnedenko.
%\newblock Sur la distribution limite du terme maximum d'une s\'{e}rieal\'{e}atoire.
%\newblock {\em Ann. Math.}, {\bf 44}, 423--453, 1943.
\bibitem{Andel}And\v{e}l, J., {\em Z\'aklady matematick\'e statistiky}. Matfyzpress, Praha, 2005.
\bibitem{Anderson1962}Anderson, T. W., {\em On the distribution of the two-sample Cram\'er-von Mises criterion}. The Annals of Mathematical Statistics, Vol. 33, No. 3, pp. 1148-1159, Sep. 1962.
\bibitem{AndersonDarling1952}Anderson, T. W., Darling, D. A., {\em Asymptotic Theory of Certain "Goodness of Fit" Criteria Based on Stochastic Processes}. The Annals of Mathematical Statistics, Vol. 23, No. 2., pp. 193-212, 1952.
\bibitem{AndersonDarling1954}Anderson, T. W., Darling, D. A., {\em A test of goodness of fit}. Journal of the American Statistical Association, Vol. 49, pp. 765-769, Dec 1954.
\bibitem{Antoch92}Antoch, J., Vorl\'i\v{c}kov\'a, D., {\em Vybran\'e metody statistick\'e anal\'yzy dat}. Academia, Praha, 1992.
\bibitem{jointMass}ATLAS, CDF, CMS and D0 Collaborations, {\em First combination of Tevatron and LHC measurements of the top-quark mass}. \texttt{arXiv:1403.4427v1 [hep-ex]}, March 2014.
\bibitem{Basu}Basu, A., Harris, I. R., Hjort, N. L., Jones M.C. {\em Robust and efficient estimation by minimising a density power divergence}. Biometrika, 85, pp. 549-559, 1998.
\bibitem{Decomposable2011}Broniatowski, M., Toma, A., Vajda, I. {\em Decomposable pseudo-distances and Applications in Statistical Estimation}. arXiv:1104.1541v1, 2011.
\bibitem{Vajda2009}Broiatowski, M., Vajda, I. {\em Several Aplications of Divergence Criteria in Continuous Families}. Research report No 2257 September 2009, \'{U}TIA AV \v{C}R, Praha, 2009.
\bibitem{Demut2010}Demut, R.{\em Robust properties of minimum divergence density estimators}. Diploma thesis, \v{C}VUT, Praha, 2010.
%\bibitem{Lecuyer}L'Ecuyer, P. {\em Efficient and Portable Combined Random Number Generators}, Communications of the ACM, 1988.
\bibitem{Devroye}Devroye, L., Gyorfi, L., Lugosi, G. {\em A Probabilistic Theory of Pattern Recognition}. Springer New York, 1996.
\bibitem{Doane1976}Doane, D. P., {\em Aesthetic frequency classification}. American Statistician, Vol. 30, pp. 181-183, 1976.
\bibitem{Heinson}Heinson, A., {\em Feynman Diagrams for talks}. [cited 04/24/2014], 2011. \\ \href{http://www-d0.fnal.gov/Run2Physics/top/top_public_web_pages/top_feynman_diagrams.html}{\texttt{http://www-d0.fnal.gov/Run2Physics/top/top\_public\_web\_pages/top\_feynman}} \\
\href{http://www-d0.fnal.gov/Run2Physics/top/top_public_web_pages/top_feynman_diagrams.html}{\texttt{\_diagrams.html}}\\
\bibitem{LieseVajda1987}Liese, F., Vajda, I., {\em Convex Statistical Distances}. Teubner, Leipzig, 1987.
\bibitem{LieseVajda}Liese, F., Vajda, I. {\em On Divergences and Informations in Statistics and Information Theory}. IEEE Transactions on Information Theory, Vol. 52, No. 10, pp. 4394-4412, 2006.
\bibitem{Menendez1995} Menéndez, M. L., Morales, D., Pardo, L., Salicrú, M., {\em Asymptotic behaviour and statistical applications of divergence measures in multinomial populations: A unified study}. Statistical Papers, Vol. 36, pp. 1-29, 1995.
\bibitem{Pettitt1976}Pettitt, A. N., {\em A two-sample Anderson-Darling rank statistic}. Biometrika, 63, pp. 161-168, 1976.
\bibitem{Renyi1961} R\'enyi, A., {\em On measures of entropy and information}. Proceedings of Fourth Berkeley Symposium on Mathematical Statistics and Probability, Vol. 1, pp. 547-561, 1961.
\bibitem{RiceRule} Lane, D. M., {\em Histograms}. [cited 04/23/2014], \\
\href{http://onlinestatbook.com/2/graphing_distributions/histograms.html}{\texttt{http://onlinestatbook.com/2/graphing\_distributions/histograms.html}}
\bibitem{Rosenblatt1952} Rosenblatt, M., {\em Limit theorems associated with variants of the con Mises statistic}., Annuals Mathematical Statistics, Vol. 30, pp. 420-447, 1952.
\bibitem{Scott1979} Scott, D. W., {\em On optimal and data-based histograms}. Biometrika 66 (3), pp. 605–610, 1979.
\bibitem{Sholz1986} Sholz, F. W., Stephens, M. A., {\em K-sample Anderson-Darling tests of fit, for continuous and discrete cases}. Technical report No. 81, University of Washington, May 1986.
\bibitem{Smirnov1944}Smirnov, N. J., {\em Pribli\v{z}enije zakonov raspredelenija slu\v{c}ajnych veli\v{c}in po empiri\v{c}eskim dannym}. Usp. mat nauk, 10, pp. 179-206.
\bibitem{Sturges1926} Sturges, H. A., {\em The choice of a class interval}. Journal of the American Statistical Association, pp. 65-66, 1926.
\bibitem{Vajda1995}Vajda, I. {\em Information - Theoretic Methods in Statistics}. Research report No. 1834 March 1995, \'{U}TIA AV \v{C}R, Praha, 1995.
\bibitem{Virius98}Virius, M. {\em Aplikace matematick\'e statistiky, metoda Monte Carlo}. \v{C}VUT, Praha, 1998.
\bibitem{Yuntse}Tsai, Yun-Tse, {\em Measurement of Electroweak Top Quark Production at} $D\mathit{\emptyset}$. Disertation, University of Rochester, 2013.
\end{thebibliography}