\documentclass[vecphys]{svmult}
\usepackage{color}
%\usepackage{makeidx}
%\usepackage{graphicx}           % standard LaTeX graphics tool when including figure files
\usepackage{multicol}           % used for the two-column index
\usepackage[bottom]{footmisc}   % places footnotes at page bottom
\usepackage[utf8]{inputenc}
\usepackage[czech]{babel}
\usepackage[T1]{fontenc}
\usepackage{sans}
\usepackage{mathrsfs}

\textheight 20 cm

\definecolor{seda}{rgb}{0.3,0.4,0.4}
\definecolor{cihlova}{rgb}{0.7969,0.1992,0}
\definecolor{tyrkys}{rgb}{0,0.5,1}
\definecolor{fialova}{rgb}{0.8,0.2,0.6}
\definecolor{zelena}{rgb}{0.063,0.761,0.078}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Title of the conference talk and appropriate paper: Testování robustnosti a eficience Renyiho divergenčních odhadů hustot pravděpodobnosti
\title*{\textcolor{fialova}{Testing of robustness and efficiency of Rényi divergence estimators of probability densities}}
% Enter your Name and Surname
\author{Jan Kučera \inst{1},  Václav Kůs \inst{1}}
% Institutes of all authors, include city and country of each institute.
\institute{Department of Mathematics, Faculty of Nuclear Sciences
and Physical Engineering, Czech Technical University, Prague, Czech Republic
%
\\
%
\vspace{0.3cm}
% E-mail of presenting authors for correspondence
Email: \texttt{\textcolor{tyrkys}{kucerj28@fjfi.cvut.cz, vaclav.kus@fjfi.cvut.cz}}\\
}
\maketitle


\section*{Abstract} % Brief abstract of the conference talk and appropriate paper: (cca 10-20 sentences)

In this contribution we study Rényi pseudodistance estimators which are based on minimization of information-theoretic divergences between empirical and hypothetical probability distribution. These distances are more robust (than e.g. MLE estimators) against outliers and other measurement errors potentially present in the data sets. Robustness of these estimators is described by influence function. In \cite{Vajda2009} and \cite{Demut2010} authors found explicit formulas for enumeration of Rényi distances in normal families and for their influence functions. We focus on finding explicit formulas for other families (Weibull, Cauchy, Exponential) and finding influence functions for these estimators. 
We perform computer simulations for pseudorandom contaminated and uncontaminated data sets, different sample sizes and different Rényi distance parameters. 
% Keywords (at most 5):
\keywords{Rényi pseudodistances; $\phi-$divergences; robustness; minimum distance estimators.}

\small
\subsection*{Acknowledgment}
This work was supported by the grants SGS12/197/OHK4/3T/14, GACR P202/10/0618, MSMT INGO-II LG12020, and by the MSMT research program under the contract MSM 6840770039.

\small
% The list of references and literature, that is important for the conference talk,
% should be placed below in alphabetical order. (at leats 3 entry)
% Please follow the format of the examples very tightly.
\begin{thebibliography}{99.}

\bibitem{Vajda2009}
Michel Broniatowski, Igor Vajda.
\newblock {\em Several Applications of Divergence Criteria in Continuous Families}.
\newblock Research report No 2257 September 2009, UTIA AV CR, Prague, 2009.

\bibitem{Vajda1995}
Igor Vajda.
\newblock {\em Information - Theoretic Methods in Statistics}.
\newblock Research report No 1834 October 1995, UTIA AV CR, Prague, 1995.

\bibitem{Decomposable2011}
Michel Broniatowski, Aida Toma, Igor Vajda.
\newblock {\em Decomposable Pseudodistances and Applications in Statistical Estimation}.
\newblock arXiv:1104.1541v1, 2011.

\bibitem{Demut2010}
Radim Demut
\newblock {\em Robust properties of minimum divergence density estimators}.
\newblock Diploma Thesis, ČVUT, Prague 2010.

\bibitem{BasuHarris}
By Ayanendranath Basu, Ian R. Harris, Nils L. Hjort, M. C. Jones
\newblock {\em Robust and eficient estimation by minimising a density power divergence}.
\newblock In Biometrika, 85, 549-559, 1998.

\bibitem{LieseVajda}
Friedrich Liese, Igor Vajda.
\newblock {\em On Divergences and Informations in Statistics and Information Theory}.
\newblock IEEE Transactions on Information Theory, Vol. 52, No. 10,4394-4412, 2006.

\end{thebibliography}

\end{document}
